Exact asymptotic expressions for local clustering in hyperbolic random graphs

### 2018-11-06 proof_overview.tex
explanation for exponential density on page 15

Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$. \PvdH{Could someone add an intuition or better explanation why this is the case.}

>>>>

Finally, we note that the height $y$ of a randomly sampled point has the exponential density $\alpha e^{-\alpha y}$: the distribution function of the radial coordinate of a vertex sampled in the disk is $\frac{\cosh(\alpha  r)-1}{\cosh(\alpha R)-1}$ which is asymptotically equivalent to $e^{\alpha(r-R)} = e^{-\alpha y}$, if $r$ and $R$ are large, resp. tending to infinity and $y=R-r$ and because of the minus sign in front of the $r$, the distribution function in $r$ turns into the complementary distribution function of $y$, from which we recognize the exponential distribution with parameter $\alpha$.%\PvdH{Could someone add an intuition or better explanation why this is the case.}
